### 2024-11-02 scripts/05-exploratory_data_analysis.qmd
paper structure updated
paper  structure updated
Updated test simulated and analysis data
fixed bugs and changed preambles

@@

  slice_head(n = 3)                       

@@

# Calculate feature values for each candidate
trump_features <- select_feature_value(trump_test, "Donald Trump")
harris_features <- select_feature_value(harris_test, "Kamala Harris")

>>>>

Trump_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Trump.parquet"))
Harris_test <- read_parquet(here::here("data/02-analysis_data/02-testing/test_Harris.parquet"))

@@

  slice_head(n = 5)                       

@@

# Calculate feature values for each candidate
trump_features <- select_feature_value(Trump_test, "Donald Trump")
harris_features <- select_feature_value(Harris_test, "Kamala Harris")
